A Linear Solution of the Linearity Challenge

### 2025-12-24 paper/Examples.lagda.tex
sync examples with code

For the encoding of the echo server (\Cref{ex:echo}), it is convenient to
introduce the linear implication connective according to the standard definition
$A \multimap B \eqdef \dual{A} \Par B$.

\begin{code}
_⊸_ : ∀{n} → PreType n → PreType n → PreType n
A ⊸ B = dual A ⅋ B
\end{code}

Recall that the server is polymorphic in the sense that the type of the value it
receives and sends back is arbitrary and denoted by a type variable $X$. The
notation $\AgdaFunction{\#}~n$ is defined in Agda's standard library and creates
an element of \AgdaDatatype{Fin} from the natural number $n$.

\begin{code}
Echo : let X = var (# 0) in
       Proc [ `! (`∀ (X ⊸ X)) ]
Echo = curry∗ server ch (< ≫)
             ( un-[]
             , curry∗ all ch (< ≫) λ X →
               curry∗ join ch (< ≫) $
               curry∗ link ch (< ≫) ch)
\end{code}

@@

\begin{code}
Echo-True : Proc [ 𝔹 ]
Echo-True = curry∗ cut Echo ≫ $
            curry∗ client ch (< ≫) $
            curry∗ ex ch (< ≫) $
            curry∗ fork ch (< ≫) $ True ⟨ ≫ ⟩ curry∗ link ch (< ≫) ch
\end{code}

>>>>

For the encoding of the echo server (\Cref{ex:echo}), recall that the server is
polymorphic in the sense that the type of the value it receives and sends back
is arbitrary and denoted by a type variable $X$. The notation
$\AgdaFunction{\#}~n$ is defined in Agda's standard library and creates an
element of \AgdaDatatype{Fin} from the natural number $n$.

\begin{code}
Echo : let X = var (# 0) in
       Proc [ `! (`∀ (X ⅋ (dual X ⊗ 𝟙))) ]
Echo = curry∗ server ch (< ≫)
             ( un-[]
             , curry∗ all ch (< ≫) λ X →
               curry∗ join ch (< ≫) $
               curry∗ (curry∗ fork ch (< ≫)) (curry∗ link ch (< > •) ch) (< ≫) $
               close ch )
\end{code}

@@

\begin{code}
Echo-True : Proc [ 𝔹 ]
Echo-True = curry∗ cut Echo ≫ $
            curry∗ client ch (< ≫) $
            curry∗ (ex {_} {dual 𝔹}) ch (< ≫) $
            curry∗ (curry∗ fork ch (< ≫)) True ≫ $
            curry∗ join ch (< ≫) $
            curry∗ wait ch (< ≫) $
            curry∗ link ch (< > •) ch
\end{code}
